### 2014-05-05 Docs/FAQ/faq.tex

@@

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = F
\end{verbatim}

@@

  Setting general convergence criteria for multigrid is as much
  art as science. 
  First, it is important to determine if the multigrd solver is
  close to convergence and just dancing around near the desired
  tolerance, but never reaching it, or if it is no where near 
  convergence.  For the latter, it may be that the multigrid
  solver was fed bad data and the problem arose in one of the earlier
  steps.  To get more detail information from the multigrid solver,
  set {\tt mg\_verbose} to a positive integer from 1-4 (the higher
  the number the more information you receive.

>>>>

\item {\em {\tt make} issues an error like:
       {\small
       \begin{verbatim}
       .../BoxLib/Tools/F_mk/GMakeMPI.mak:40: Extraneous text after `else' directive
       .../BoxLib/Tools/F_mk/GMakeMPI.mak:47: *** only one `else' per conditional.  Stop
      \end{verbatim}
      }
      }

   You need to use GNU make version 3.81 or later.  Earlier versions do
   not support an {\em else-if} clause.

@@

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = F
\end{verbatim}
\runparamidx{max\_step}
\runparamidx{init\_iter}
\runparamidx{init\_divu\_iter}
\runparamidx{do\_initial\_projection}

@@

  Setting general convergence criteria for multigrid is as much
  art as science. 
  First, it is important to determine if the multigrd solver is
  close to convergence and just dancing around near the desired
  tolerance, but never reaching it, or if it is no where near 
  convergence.  For the latter, it may be that the multigrid
  solver was fed bad data and the problem arose in one of the earlier
  steps.  To get more detail information from the multigrid solver,
  set \runparam{mg\_verbose} to a positive integer from 1-4 (the higher
  the number the more information you receive.

### 2014-05-05 Docs/architecture/architecture.tex

    The various problem-setups.  Each problem in \maestro\ gets it own
    sub-directory under {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
      UNIT\_TESTS/}.  The {\tt GNUmakefile} in the problem directory
    includes the instructions on how to build the executable,
    including what modules in {\tt Microphysics/} are used.  Any file that
    you place in a sub-directory here takes precedence over a file of
    the same name in {\tt MAESTRO/}.  This allows problems to have
    custom versions of the main \maestro\ routines (e.g.\ initial
    conditions via {\tt initdata.f90}.  See \S~\ref{sec:makefile} and
    Chapter~\ref{ch:make} for details on the build system).

@@

      Special \maestro\ problem directories that test only a single
      component of the \maestro\ algorithm.  These often have their
      own main drivers ({\tt varden.f90}) that setup and initialize
      some data structures and then call only a few of the
      \maestro\ routines.  See Chapter~\ref{chapter:unit_tests} for details.

@@

Runtime parameters listed in the {\tt MAESTRO/\_parameters} file are
parsed at compile time and the file {\tt probin.f90} is written and
compiled.  This is a Fortran module that holds the values of the
runtime parameters and makes them available to any routine.  By
default, the build system looks for a file called {\tt \_parameters}
in the problem directory and adds those parameters along with the
master list of \maestro\ parameters ({\tt MAESTRO/\_parameters}) to
the {\tt probin\_module}.

@@

The runtime parameters for the core \maestro\ algorithm are listed in
{\tt MAESTRO/\_parameters}.  That file is parsed at compile-time by
the {\tt MAESTRO/write\_probin.py} script (along with any
problem-specific parameters).  The script outputs the {\tt probin.f90}
source file.  Each line in the {\tt \_parameters} file has the form:
\vskip 3mm
{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value} 
\vskip 3mm
\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and are used to produce documentation about the
available runtime parameters.  For the documentation, runtime parameters are grouped together
in the {\tt \_parameters} file into categories.  The category headings
are defined by comments in the {\tt \_parameters} file and any comments
following that heading are placed into that category.  The documentation
(Chapter~\ref{ch:parameters}) is produced by the script 
{\tt MAESTRO/docs/runtime\_parameters/rp.py}.

At runtime, the default values for the parameters can be overridden
either through the inputs file (by adding a line of the form: {\tt
  parameter = value}) or through a command-line argument (taking the
form: {\tt --parameter value}).  The {\tt probin\_module} makes the
values of the runtime parameters available to the various functions
in the code (see \S~\ref{sec:probin}).

@@

\maestro\ initial models are read in by the {\tt Util/model\_parser}
routines.  This expects the initial model to contain a header giving
the number of variables and their names, followed by rows of data
giving the coordinate and data values at that coordinate.  The initial
model should contain the same species data (in the form of mass fractions) as
defined in the {\tt network} module used by the \maestro\ problem.

@@

The best way to customize the initialization (e.g.\ add perturbations)
is to copy from one of the existing problems.  The file {\tt
  initveldata.f90} controls the velocity field initialization and {\tt
  initscaldata.f90} controls the initialization of the scalars
($\rho$, $\rho X_k$, $\rho h$).  The {\tt test2} problem is a good
starting point for plane-parallel and {\tt wdconvect} is a good
starting point for full stars.

@@

A common operation on a \multifab\ is to initialize it to $0$
everywhere.  This can be done (level-by-level) as
\begin{lstlisting}[language={[95]fortran},mathescape=false]
call setval(mfab(n), ZERO, all=.true.)
\end{lstlisting}
where {\tt ZERO} is the constant 0.0 from {\tt bl\_constants\_module}.

The procedure for accessing the data in each grid managed by the \multifab\
is shown in \S~\ref{sec:example}.  
Subroutines to add, multiply, or divide two \multifab s exist, as do
subroutines to copy from one \multifab\ to another---see {\tt boxlib/multifab.f90}
for the full list of routines that work with \multifab s.

When you are done working with a \multifab, its memory can be freed by
calling {\tt multifab\_destroy} on the \multifab.

@@

Individual state variables should be indexed using the integer keys
provided by the {\tt variables} module (see \S
\ref{sec:variables_module}).  For example, the integer {\tt rho\_comp}
will always refer to the density component of the state.

@@

The {\tt average\_module} module provides a routine {\tt average} that takes
a multilevel \multifab\ array and averages the full Cartesian data
onto the 1D base state.

@@

The {\tt eos\_module} provides the interface to the equation of 
state to connect the state variables thermodynamically.  It 
gets the information about the fluid species from the {\tt network}
module (for example, the atomic number, $Z$, and atomic weight, $A$,
of the nuclei).

@@

The thermodynamic quantities are stored in a Fortran type {\tt eos\_t},
which has fields for all the thermodynamic inputs and outputs.  The 
type definition is brought in through {\tt eos\_type\_module}.
\footnote{ Note: an older interface to the EOS exists, but is
  deprecated.  In this mode, the {\tt eos\_old\_interface} module declares 
  the variables that need appear in the old-style {\tt eos} call
  argument list.  \maestro\ routines use these module variables in the
  EOS call to avoid having to declare each quantity in each routine
  that calls the EOS.  Most code has been updated to use the new interface.}

@@

The {\tt fill\_3d\_module} provides routines that map from the 1D
base state to the full Cartesian 2- or 3D state.  Variations in the
routines allow for cell-centered or edge-centered data on either the
base state or full Cartesian state.

@@

The {\tt fundamental\_constants\_module} provides a simple list of
various fundamental constants (e.g.\ Newton's gravitational constant)
in CGS units.

@@

The {\tt network} module defines the number species advected by the
code ({\tt nspec}), their ordering, and gives their basic properties
(like atomic number, $Z$, and atomic mass, $A$).  All \maestro\ problems
require a {\tt network} module, even if there are no reactions
modeled.  Many different reaction modules (containing different sets
of isotopes) exist in {\tt Microphysics/networks}.  The particular network
used by a problem is defined in the problem's {\tt GNUmakefile}.

@@

{\tt probin\_module} provides access to the runtime parameters.
The runtime parameters appear simply as module variables.  To get the 
value of a parameter, one simply needs to `{\tt use probin\_module}'.
The preferred method is to add the `{\tt only}' clause to the
{\tt use} statement and explicitly list only those parameters that
are used in the routine.  Defining new runtime parameters is
described in \S~\ref{sec:def_runtime_param}.

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are list in table~\ref{arch:table:variables}.

@@

The species indices are contiguous in the state array, spanning {\tt
  spec\_comp:spec\_comp-1+nspec}.  To find a particular species, a
query can be made through the {\tt network} module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.
The {\tt variables} module also provides keys for the plotfile
variables and boundary condition types.

@@

All MPI calls are wrapped by functions in the {\tt parallel} module.  For
serial jobs, the wrappers simply do the requested operation on processor.
By wrapping the calls, we can easily switch between serial and parallel
builds.

@@

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic BoxLib data types. Specifically, here, {\tt
  bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt ml\_layout\_module} defines the
datatype for a \mllayout---many routines will take an \mllayout
to allow us to fill ghostcells.  The {\tt variables} module is a \maestro\
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.

@@

Each multifab can have their own number of ghostcells, so we get
these next:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    ng_sp = nghost(s(1))
    ng_um = nghost(umac(1,1))
\end{lstlisting}
By convention, all levels in a given multifab have the same number of
ghostcells, so we use level 1 in the {\tt nghost()} call.  We also use
the same number of ghostcells for each component of the velocity, so
we only need to consider the first component in the {\tt nghost()}
call.  The ghostcells will be needed to access the data stored in the
\fab s.

To access the data, we loop over all the levels, and all the boxes in
the given level.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    do n=1,nlevs
       do i = 1, nfabs(s(n))
\end{lstlisting}
{\tt nfabs(s(n))} is simply the number of boxes in level {\tt n} on
the current processor.  Each processor knows which \fab s in its
\multifab are local to that processor, and this loop will only loop
over those.

@@

\noindent In this function, the bounds of the {\tt density} array take
into account the {\tt ng\_sp} ghostcells and the index space of the
current box.  Likewise, the MAC velocities refer to the {\tt ng\_um}
ghostcells.  The {\tt j} and {\tt i} loops loop over all the valid
zones.  Coordinate information is computed from {\tt dx} and {\tt
  prob\_lo} which is the physical lower bound of the domain.  {\tt
  bl\_constants\_module} declares useful double-precision constants,
like {\tt HALF} (0.5).  Here, we see how to access the density for
the current zone and compute the cell-centered velocities from the
MAC velocities.  By convection, for a nodal array, the indices refer 
to the {\em lower} interface in the nodal direction, so for {\tt umac},
{\tt umac(i,j)} and {\tt umac(i+1,j)} are the $x$ MAC velocities
on the lower and upper edge of the zone in the $x$-direction.

@@

\item {\tt multifab\_fill\_boundary} fills ghost cells for two
  adjacent grids at the same level, which als includes periodic domain
  boundary ghost cells.

\item {\tt multifab\_physbc} fills ghostcells at the physical boundaries.

\item {\tt multifab\_fill\_ghost\_cells} is used for multilevel
  problems, and fills ghostcells in the finer grid (level {\tt n}) by
  interpolating from data in the coarser grid (level {\tt n-1}).
  This function, by default, will also call {\tt multifab\_fill\_boundary}
  and {\tt multifab\_physbc} for both levels {\tt n} and {\tt n-1} (you 
  can override this behavior for speed optimization purposes).
  This call is usually preceded by a call to 
  {\tt ml\_cc\_restriction\_c} which sets the level {\tt n-1} data to be
  the average of the level {\tt n} data covering it.

@@

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, the array {\tt adv\_bc\_level\_array}
describes the {\em action} taken (e.g.\ reflect, extrapolate, etc.)
for each variable when filling boundaries.  {\tt
  adv\_bc\_level\_array} specifically describes the boundary
conditions that are in play for the advection (hyperbolic) equations.
The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the additional
component, {\tt nvar}, allows for each state variable that lives on a
grid to have different boundary condition actions associated with it.
The convention is that the first {\tt dm} variables in \bclevel (where {\tt dm} is
the dimensionality of the simulation) refer to the
velocity components, and the subsequent slots are for the other
standard variables described in the {\tt variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

@@

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the {\tt
  multifab\_physbc} routine.  When you have an {\tt EXT\_DIR}
condition in {\tt multifab\_physbc} (an specified in the inputs file
as {\tt inlet}), the advection solver (via the slope routine) and
linear solvers will then assume that the value in the ghost cells is
equal to the value that actually lies on the wall.

@@

\maestro\ has support for Lagrangian particles that are passively
advected with the velocity field.  These are useful for diagnostics
and post-processing.  To use particles, particles must be seeded into
the domain by writing a problem-specific {\tt init\_particles.f90}
routine.  This routine is called at the start of the simulation.  The
{\tt init\_particles} routines add particles at specific locations by
calling the {\tt particle\_module}'s {\tt add} routine when a given
criteria is met by the fluid state.

>>>>

    The various problem-setups.  Each problem in \maestro\ gets it own
    sub-directory under {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
      UNIT\_TESTS/}.  The {\tt GNUmakefile} in the problem directory
    includes the instructions on how to build the executable,
    including what modules in {\tt Microphysics/} are used.  Any file that
    you place in a sub-directory here takes precedence over a file of
    the same name in {\tt MAESTRO/}.  This allows problems to have
    custom versions of the main \maestro\ routines (e.g.\ initial
    conditions via \code{initdata.f90}.  See \S~\ref{sec:makefile} and
    Chapter~\ref{ch:make} for details on the build system).

@@

      Special \maestro\ problem directories that test only a single
      component of the \maestro\ algorithm.  These often have their
      own main drivers (\code{varden.f90}) that setup and initialize
      some data structures and then call only a few of the
      \maestro\ routines.  See Chapter~\ref{chapter:unit_tests} for details.

@@

Runtime parameters listed in the {\tt MAESTRO/\_parameters} file are
parsed at compile time and the file \code{probin.f90} is written and
compiled.  This is a Fortran module that holds the values of the
runtime parameters and makes them available to any routine.  By
default, the build system looks for a file called {\tt \_parameters}
in the problem directory and adds those parameters along with the
master list of \maestro\ parameters ({\tt MAESTRO/\_parameters}) to
the \code{probin\_module}.

@@

The runtime parameters for the core \maestro\ algorithm are listed in
{\tt MAESTRO/\_parameters}.  That file is parsed at compile-time by
the {\tt MAESTRO/write\_probin.py} script (along with any
problem-specific parameters).  The script outputs the \code{probin.f90}
source file.  Each line in the {\tt \_parameters} file has the form:
\vskip 3mm
{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value} 
\vskip 3mm
\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and are used to produce documentation about the
available runtime parameters.  For the documentation, runtime parameters are grouped together
in the {\tt \_parameters} file into categories.  The category headings
are defined by comments in the {\tt \_parameters} file and any comments
following that heading are placed into that category.  The documentation
(Chapter~\ref{ch:parameters}) is produced by the script 
{\tt MAESTRO/docs/runtime\_parameters/rp.py}.

At runtime, the default values for the parameters can be overridden
either through the inputs file (by adding a line of the form: {\tt
  parameter = value}) or through a command-line argument (taking the
form: {\tt --parameter value}).  The \code{probin\_module} makes the
values of the runtime parameters available to the various functions
in the code (see \S~\ref{sec:probin}).

@@

\maestro\ initial models are read in by the \code{Util/model\_parser}
routines.  This expects the initial model to contain a header giving
the number of variables and their names, followed by rows of data
giving the coordinate and data values at that coordinate.  The initial
model should contain the same species data (in the form of mass fractions) as
defined in the \code{network} module used by the \maestro\ problem.

@@

The best way to customize the initialization (e.g.\ add perturbations)
is to copy from one of the existing problems.  The file \code{initveldata.f90} controls the velocity field initialization and \code{initscaldata.f90} controls the initialization of the scalars
($\rho$, $\rho X_k$, $\rho h$).  The {\tt test2} problem is a good
starting point for plane-parallel and {\tt wdconvect} is a good
starting point for full stars.

@@

A common operation on a \multifab\ is to initialize it to $0$
everywhere.  This can be done (level-by-level) as
\begin{lstlisting}[language={[95]fortran},mathescape=false]
call setval(mfab(n), ZERO, all=.true.)
\end{lstlisting}
where {\tt ZERO} is the constant 0.0 from \code{bl\_constants\_module}.

The procedure for accessing the data in each grid managed by the \multifab\
is shown in \S~\ref{sec:example}.  
Subroutines to add, multiply, or divide two \multifab s exist, as do
subroutines to copy from one \multifab\ to another---see \code{BoxLib/Src/F\_BaseLib/multifab.f90}
for the full list of routines that work with \multifab s.

When you are done working with a \multifab, its memory can be freed by
calling \code{multifab\_destroy} on the \multifab.

@@

Individual state variables should be indexed using the integer keys
provided by the \code{variables} module (see \S
\ref{sec:variables_module}).  For example, the integer {\tt rho\_comp}
will always refer to the density component of the state.

@@

The \code{average\_module} module provides a routine {\tt average} that takes
a multilevel \multifab\ array and averages the full Cartesian data
onto the 1D base state.

@@

The \code{eos\_module} provides the interface to the equation of 
state to connect the state variables thermodynamically.  It 
gets the information about the fluid species from the \code{network}
module (for example, the atomic number, $Z$, and atomic weight, $A$,
of the nuclei).

@@

The thermodynamic quantities are stored in a Fortran type {\tt eos\_t},
which has fields for all the thermodynamic inputs and outputs.  The 
type definition is brought in through \code{eos\_type\_module}.
\footnote{ Note: an older interface to the EOS exists, but is
  deprecated.  In this mode, the {\tt eos\_old\_interface} module declares 
  the variables that need appear in the old-style \code{eos} call
  argument list.  \maestro\ routines use these module variables in the
  EOS call to avoid having to declare each quantity in each routine
  that calls the EOS.  Most code has been updated to use the new interface.}

@@

The \code{fill\_3d\_module} provides routines that map from the 1D
base state to the full Cartesian 2- or 3D state.  Variations in the
routines allow for cell-centered or edge-centered data on either the
base state or full Cartesian state.

@@

The \code{fundamental\_constants\_module} provides a simple list of
various fundamental constants (e.g.\ Newton's gravitational constant)
in CGS units.

@@

The \code{network} module defines the number species advected by the
code ({\tt nspec}), their ordering, and gives their basic properties
(like atomic number, $Z$, and atomic mass, $A$).  All \maestro\ problems
require a {\tt network} module, even if there are no reactions
modeled.  Many different reaction modules (containing different sets
of isotopes) exist in {\tt Microphysics/networks}.  The particular network
used by a problem is defined in the problem's {\tt GNUmakefile}.

@@

\code{probin\_module} provides access to the runtime parameters.
The runtime parameters appear simply as module variables.  To get the 
value of a parameter, one simply needs to `{\tt use probin\_module}'.
The preferred method is to add the `{\tt only}' clause to the
{\tt use} statement and explicitly list only those parameters that
are used in the routine.  Defining new runtime parameters is
described in \S~\ref{sec:def_runtime_param}.

@@

The \code{variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are list in table~\ref{arch:table:variables}.

@@

The species indices are contiguous in the state array, spanning {\tt
  spec\_comp:spec\_comp-1+nspec}.  To find a particular species, a
query can be made through the \code{network} module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.
The \code{variables} module also provides keys for the plotfile
variables and boundary condition types.

@@

All MPI calls are wrapped by functions in the \code{parallel} module.  For
serial jobs, the wrappers simply do the requested operation on processor.
By wrapping the calls, we can easily switch between serial and parallel
builds.

@@

\noindent Here, the {\tt bl\_types} and \code{multifab\_module}
modules bring in the basic BoxLib data types. Specifically, here,
\code{bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and \code{multifab\_module} defines
the \multifab\ data type.  The \code{ml\_layout\_module} defines the
datatype for a \mllayout---many routines will take an \mllayout to
allow us to fill ghostcells.  The \code{variables} module is a
\maestro\ module that provides integer keys for indexing the state
arrays.  In this case the integer {\tt rho\_comp} refers to the
location in the state array corresponding to density.

@@

Each multifab can have their own number of ghostcells, so we get
these next:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    ng_sp = nghost(s(1))
    ng_um = nghost(umac(1,1))
\end{lstlisting}
By convention, all levels in a given multifab have the same number of
ghostcells, so we use level 1 in the \code{nghost()} call.  We also use
the same number of ghostcells for each component of the velocity, so
we only need to consider the first component in the {\tt nghost()}
call.  The ghostcells will be needed to access the data stored in the
\fab s.

To access the data, we loop over all the levels, and all the boxes in
the given level.
\begin{lstlisting}[language={[95]fortran},mathescape=false]
    do n=1,nlevs
       do i = 1, nfabs(s(n))
\end{lstlisting}
\code{nfabs(s(n))} is simply the number of boxes in level {\tt n} on
the current processor.  Each processor knows which \fab s in its
\multifab are local to that processor, and this loop will only loop
over those.

@@

\noindent In this function, the bounds of the {\tt density} array take
into account the {\tt ng\_sp} ghostcells and the index space of the
current box.  Likewise, the MAC velocities refer to the {\tt ng\_um}
ghostcells.  The {\tt j} and {\tt i} loops loop over all the valid
zones.  Coordinate information is computed from {\tt dx} and {\tt
  prob\_lo} which is the physical lower bound of the domain.
\code{bl\_constants\_module} declares useful double-precision
constants, like {\tt HALF} (0.5).  Here, we see how to access the
density for the current zone and compute the cell-centered velocities
from the MAC velocities.  By convection, for a nodal array, the
indices refer to the {\em lower} interface in the nodal direction, so
for {\tt umac}, {\tt umac(i,j)} and {\tt umac(i+1,j)} are the $x$ MAC
velocities on the lower and upper edge of the zone in the
$x$-direction.

@@

\item \code{multifab\_fill\_boundary} fills ghost cells for two
  adjacent grids at the same level, which als includes periodic domain
  boundary ghost cells.

\item \code{multifab\_physbc} fills ghostcells at the physical boundaries.

\item \code{multifab\_fill\_ghost\_cells} is used for multilevel
  problems, and fills ghostcells in the finer grid (level {\tt n}) by
  interpolating from data in the coarser grid (level {\tt n-1}).
  This function, by default, will also call {\tt multifab\_fill\_boundary}
  and {\tt multifab\_physbc} for both levels {\tt n} and {\tt n-1} (you 
  can override this behavior for speed optimization purposes).
  This call is usually preceded by a call to 
  \code{ml\_cc\_restriction\_c} which sets the level {\tt n-1} data to be
  the average of the level {\tt n} data covering it.

@@

Whereas {\tt phys\_bc\_level\_array} provides a physical description
of the type of boundary, the array {\tt adv\_bc\_level\_array}
describes the {\em action} taken (e.g.\ reflect, extrapolate, etc.)
for each variable when filling boundaries.  {\tt
  adv\_bc\_level\_array} specifically describes the boundary
conditions that are in play for the advection (hyperbolic) equations.
The form of this array is {\tt
  adv\_bc\_level\_array(0:ngrids,dim,2,nvar)} where the additional
component, {\tt nvar}, allows for each state variable that lives on a
grid to have different boundary condition actions associated with it.
The convention is that the first {\tt dm} variables in \bclevel (where {\tt dm} is
the dimensionality of the simulation) refer to the
velocity components, and the subsequent slots are for the other
standard variables described in the \code{variables\_module}.  For
instance, to reference the boundary condition for density, one would
index with {\tt dm+rho\_comp}.  For temporary variables that are
created on the fly in the various routines in \maestro\ there may not
be a variable name in {\tt variables\_module} that describes the
temporary variable.  In this case, the special variables {\tt
  foextrap\_comp} and {\tt hoextrap\_comp} (first-order and high-order
extrapolation) are used.

@@

The actual filling of the ghostcells according to the descriptions
contained in the \bctower\ is carried out by the \code{multifab\_physbc} routine.  When you have an {\tt EXT\_DIR}
condition in {\tt multifab\_physbc} (an specified in the inputs file
as {\tt inlet}), the advection solver (via the slope routine) and
linear solvers will then assume that the value in the ghost cells is
equal to the value that actually lies on the wall.

@@

\maestro\ has support for Lagrangian particles that are passively
advected with the velocity field.  These are useful for diagnostics
and post-processing.  To use particles, particles must be seeded into
the domain by writing a problem-specific \code{init\_particles.f90}
routine.  This routine is called at the start of the simulation.  The
{\tt init\_particles} routines add particles at specific locations by
calling the \code{particle\_module}'s {\tt add} routine when a given
criteria is met by the fluid state.

### 2014-05-05 Docs/flowchart/flowchart.tex

\section{Time Advancement Algorithm}\label{Sec:Time Advancement Algorithm}
Here is the current description of the algorithm, based from the
description in the multilevel paper.  The initialization has also been
included with more detail than was given in paper III.  The main
driver for a single step of the algorithm is {\tt advance.f90}---refer
to that code to see the sequence of functions called to implement each
step.

@@

\item {\em ``Divu'' iterations}: Next we do \runparam{init\_divu\_iter} iterations 
  to project the velocity field using a constraint that sees reactions
  and external heating. 
  The initial timestep estimate is provided by {\tt firstdt} and
  $\Ub^{0,0}$, to allow us to compute the effect of reactions over $\Delta t/2$.

>>>>

\section{Time Advancement Algorithm}\label{Sec:Time Advancement Algorithm}
Here is the current description of the algorithm, based from the
description in the multilevel paper.  The initialization has also been
included with more detail than was given in paper III.  The main
driver for a single step of the algorithm is \code{advance.f90}---refer
to that code to see the sequence of functions called to implement each
step.

@@

\item {\em ``Divu'' iterations}: Next we do \runparam{init\_divu\_iter} iterations 
  to project the velocity field using a constraint that sees reactions
  and external heating. 
  The initial timestep estimate is provided by \code{firstdt} and
  $\Ub^{0,0}$, to allow us to compute the effect of reactions over $\Delta t/2$.

### 2014-05-05 Docs/getting_started/getting_started.tex

By default, \maestro\ outputs global diagnostics each timestep into a
file called {\tt maestro\_diag.out}.  This includes the maximum Mach
number, peak temperature, and peak nuclear energy generation rate.
Individual problems can provide their own {\tt diag.f90} file to
produce custom diagnostic output.  This information can be plotted
directly with {\sf GNUplot}, for example.

@@

  The string-based parameters are a newer option for specifying
  boundary conditions, and are preferred due to clarity.  The
  conversion between the string names and integer flags is done
  by \boxlib\ in the {\tt bc\_module} at the time of initializing
  the runtime parameters.

>>>>

By default, \maestro\ outputs global diagnostics each timestep into a
file called {\tt maestro\_diag.out}.  This includes the maximum Mach
number, peak temperature, and peak nuclear energy generation rate.
Individual problems can provide their own \code{diag.f90} file to
produce custom diagnostic output.  This information can be plotted
directly with {\sf GNUplot}, for example.

@@

  The string-based parameters are a newer option for specifying
  boundary conditions, and are preferred due to clarity.  The
  conversion between the string names and integer flags is done
  by \boxlib\ in the \code{bc\_module} at the time of initializing
  the runtime parameters.

### 2014-05-05 Docs/initial_models/initial_models.tex

We deal with the edge of the star by tracking the first coarse cell 
in which the density falls below {\tt base\_cutoff\_density}.  We note 
the radius of this cell center, and the values of $\rho$, $\rho h$, $X_k$, 
$p$, and $T$ in this cells.  Then, at every level, if current cell-center 
is above this radius, we set the state equal to this stored state.  This 
ensures a consistent treatment of the edge of the star at all levels.

@@

Given $p^{\init}, \rho^{\init}, T^{\init},$ and $X^{\init}$, this
section describes how the base state ($\rho_0$ and $p_0$) and full
state ($\rho, h, X$, and $T$) are computed.  The base state is, general, not
simply a direct copy of the initial model data, since we require that
$\rho_0 = \overline\rho$.  Additionally, we require thebase state to
be HSE according to equation (\ref{HSE Discretization}), and that the full
state is thermodynamically consistent with $p_0$.  Overall we do:
\begin{enumerate}
\item Fill $\rho^{\init}, h^{\init}, X^{\init}$, and $T^{\init}$ onto a 
  multifab to obtain the full state $\rho, h, X$, and $T$.
\item If {\tt perturb\_model} = T, a user-defined perturbation is
  added.  This routine should make sure that the EOS is called so that
  there is some sense of thermodynamic consistency.
\item Set $\rho_0 = \overline\rho$.
\item Compute $p_0$ using {\tt enforce\_HSE}.
\item Compute $T,h = T,h(\rho,p_0,X_k)$.
\item Set $(\rho h)_0 = \overline{(\rho h)}$.
\item Compute $\overline{T}$.  Note that we only use $\overline{T}$ as
  a diagnostic and as a seed for EOS calls.
\end{enumerate}
Now $\rho_0 = \overline\rho$, the base state is in HSE, and the full
state is thermodynamically consistent with $p_0$.

>>>>

We deal with the edge of the star by tracking the first coarse cell 
in which the density falls below \runparam{base\_cutoff\_density}.  We note 
the radius of this cell center, and the values of $\rho$, $\rho h$, $X_k$, 
$p$, and $T$ in this cells.  Then, at every level, if current cell-center 
is above this radius, we set the state equal to this stored state.  This 
ensures a consistent treatment of the edge of the star at all levels.

@@

Given $p^{\init}, \rho^{\init}, T^{\init},$ and $X^{\init}$, this
section describes how the base state ($\rho_0$ and $p_0$) and full
state ($\rho, h, X$, and $T$) are computed.  The base state is, general, not
simply a direct copy of the initial model data, since we require that
$\rho_0 = \overline\rho$.  Additionally, we require thebase state to
be HSE according to equation (\ref{HSE Discretization}), and that the full
state is thermodynamically consistent with $p_0$.  Overall we do:
\begin{enumerate}
\item Fill $\rho^{\init}, h^{\init}, X^{\init}$, and $T^{\init}$ onto a 
  multifab to obtain the full state $\rho, h, X$, and $T$.
\item If \runparam{perturb\_model} {\tt = T}, a user-defined perturbation is
  added.  This routine should make sure that the EOS is called so that
  there is some sense of thermodynamic consistency.
\item Set $\rho_0 = \overline\rho$.
\item Compute $p_0$ using {\tt enforce\_HSE}.
\item Compute $T,h = T,h(\rho,p_0,X_k)$.
\item Set $(\rho h)_0 = \overline{(\rho h)}$.
\item Compute $\overline{T}$.  Note that we only use $\overline{T}$ as
  a diagnostic and as a seed for EOS calls.
\end{enumerate}
Now $\rho_0 = \overline\rho$, the base state is in HSE, and the full
state is thermodynamically consistent with $p_0$.
